Open Questions for Computer Science and Cheminformatics

### 2011-11-21 OpenQuestions.tex
some more edits

Can we employ modern frameworks like Hadoop to perform this? Can we
develop a generalized framework that includes the requisite
cheminformatics tools that allows users to seamless distribute jobs
over Hadoop and other map reduce systems?

Going further, are there cheminformatics problems that can make use of
the map/reduce paradigm at the algorithmic level? More generally, are
cheminformatics algorithms amenable to parallelization (that does not
involve chunking the input data)

>>>>

Can we employ modern frameworks like Hadoop to perform this? Can we
develop a generalized framework that includes the requisite
cheminformatics tools that allows users to seamlessly distribute jobs
over Hadoop and other map reduce systems?

Going further, are there cheminformatics problems that can make use of
the map/reduce paradigm at the algorithmic level? More generally, are
cheminformatics algorithms amenable to parallelization (that does not
involve chunking the input data)? Are they worth the effort?
